dendro

### 2017-05-17 analysis/test-bai.Rmd
update

>>>>

rownames(sj_tree) <- sj_tree$year
sj_tree <- sj_tree[,-1]
carwi <- detrend(rwl = ca_tree, method = "ModNegExp")
ca_prwi <- data.frame(rw = rowMeans(carwi, na.rm=TRUE))
ca_prwi <- ca_prwi %>% mutate(year = rownames(.),
                        site = as.factor('ca'),
                        rw_log = log(rw))

xx <- data.frame(rw = rowMeans(ca_tree, na.rm=TRUE))

plot(xx$rw~rownames(xx))

sjcrn <- chron(sjrwi, prefix = "rw_")
plot(sjcrn, add.spline=TRUE, nyrs=20)
plot()

sj_tree <- rw_byTree(sj)
ca_tree <- rw_byTree(ca)

rownames(ca_tree) <- ca_tree$year
ca_tree <- ca_tree[,-1]
ca_p <- data.frame(rw = rowMeans(ca_tree, na.rm=TRUE))

ca_p <- ca_p %>% mutate(year = rownames(.),
                        site = as.factor('ca'),
                        rw_log = log(rw))

rownames(sj_tree) <- sj_tree$year
sj_tree <- sj_tree[,-1]
sj_p <- data.frame(rw = rowMeans(sj_tree, na.rm=TRUE))

sj_p <- sj_p %>% mutate(year = rownames(.),
                        site = as.factor('sj'),
                        rw_log = log(rw))

xx <- rbind(ca_p, sj_p)

xx %>% ggplot(aes(x=as.Date(year, format='%Y'), y=rw_log)) + 
  geom_line(aes(group=1)) + 
  scale_x_date(date_labels = "%Y") + 
  facet_wrap(~site, ncol=1, scales = 'free_y') + 
  theme_bw() + 
  geom_vline(xintercept = as.numeric(as.Date(c('2005-06-01')))) +
  geom_vline(xintercept = as.numeric(as.Date(c('2012-06-01')))) +
  xlab('Year') + ylab('Ring width (1/100 mm)')

xx %>% filter(site =='ca') %>% 
  ggplot(aes(x=as.Date(year, format='%Y'), y=rw)) + geom_point(colour='blue') +
  geom_line(aes(group=1), colour='blue') + 
  scale_x_date(date_labels = "%Y") + 
  theme_bw() + 
  # geom_vline(xintercept = as.numeric(as.Date(c('2005-06-01')))) +
  # geom_vline(xintercept = as.numeric(as.Date(c('2012-06-01')))) +
  xlab('Year') + ylab('Ring width (1/100 mm)')

ca_prwi %>%
  ggplot(aes(x = as.Date(year, format = '%Y'), y = rw)) + geom_point() +
  geom_line(aes(group = 1)) +
  scale_x_date(date_labels = "%Y") +
  theme_bw() +
  # geom_vline(xintercept = as.numeric(as.Date(c('2005-06-01')))) +
  # geom_vline(xintercept = as.numeric(as.Date(c('2012-06-01')))) +
  xlab('Year') + ylab('Ring width Index')
